Borel regularity for ODEs and Thimble Integrals

### 2023-12-30 exp-resurgence.tex
Correction of eq 2 in the introduction check thimble integrals

@@

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{85085}{33592320} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
\color{orange}
\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
\color{black}
Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.

@@

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j^\theta$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j^\theta$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j^\theta$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j^\theta$ can be regarded as the component of $f^{-1}(\Gamma_j^\theta)$ that goes through $a_j$.  \textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity along the positive real axis.}
    \label{fig:thimble_vs_rays}
\end{figure}

Let $I_j$ be the thimble integral through the thimble $\Lambda_j^\theta$,

@@

I_j(z)\defeq\int_{\Lambda_j^\theta}e^{-zf}\nu

@@

our main results show that $I_j$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. Thus, we recall the well-known result

@@

A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}

@@

\iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right),

@@

where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}

@@

If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 

@@

\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.

@@

{I}_{j} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\

@@

\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]

@@

On the one hand, with a change of coordinates, the thimble integral $I_j$ can be written as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}. 
On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta=\alpha_j$ in the position domain. Then, we'll show that the Taylor expansion of $\iota_j$ at $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.15]{figures/cotg_singular_fibre_laplace.PNG}
    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane. However, the fiber over a singular point $s$ of $B$ has an interesting structure. Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
    \label{fig:different_fibres}
\end{figure}
We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}

On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}. In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_j$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_j\in e^{-\alpha_j z} z^{-\tau_j}\C\llbracket z^{-1}\rrbracket$, where $\tau_j=Q(-\alpha_j)/P’(-\alpha_j)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since $-\alpha_1,\ldots,-\alpha_d$ are distinct, the transmonomials $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ determine a basis up to scaling, giving the space of formal solutions a a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_j$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.

At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame. This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ (see Corollary~\ref{cor:borel_reg_ODE}). As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha_j$. Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations analytically in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).

@@

In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$. Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$. } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$. Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha_i-\alpha_j)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).

@@

When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The half-plane $z \in H_{\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.

>>>>

%% for the figure
% colors
\definecolor{smoked}{RGB}{216, 212, 204}
\definecolor{mauve}{RGB}{200, 55, 171}
\definecolor{apricot}{RGB}{250, 144, 4}
\definecolor{sky}{RGB}{66, 169, 244}
\definecolor{plum}{RGB}{76, 0, 102}

% === phase space laplace ===
\include{../figures/phase-space-laplace.tex}

@@

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}---up to a constant.\begin{verify}
    see Mathematica document.
\end{verify}

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.

@@

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a$, let $\Gamma_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\Gamma_\alpha^\theta$ which vanishes at $\alpha$. These are well-defined as long as $\Gamma_\alpha^\theta$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_\alpha^\theta$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_a^\theta$ can be regarded as the component of $f^{-1}(\Gamma_\alpha^\theta)$ that goes through $a$.  \textcolor{orange}{We could orient so that shifting $\Lambda_a$ to its left would make its projection run clockwise around $\Gamma_\alpha$. However, this only seems to be possible when $X$ is 1-dimensional.}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity along the positive real axis.}
    \label{fig:thimble_vs_rays}
\end{figure}
Choose $a$ a ciritcal point of $f$ and $\alpha=f(a)$, let $I$ be the thimble integral through the thimble $\Lambda_a^\theta$,

@@

I(z)\defeq\int_{\Lambda_a^\theta}e^{-zf}\nu

@@

our main results show that $I$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. We recall the well-known result

@@

A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}

@@

\iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda^\theta(\zeta)}\nu \right),

@@

where $\Lambda^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$. Notice that $\Lambda(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda$ needs an orientation, but the orientation is arbitrary.]}

@@

If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 

@@

\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$. Recall that $\theta$ is the direction of the ray $\Gamma^\theta_\alpha$.
\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.

@@

{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\

@@

\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]

@@

On the one hand, with a change of coordinates, the thimble integral $I$ can be written as a Laplace type integral, i.e. as the Laplace transform of a function $\iota$, written explicitly in equation~\eqref{eqn:formula}. 
On the other hand, we compute the asymptotic expansion of $I$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain. Finally, we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.

@@

\begin{figure}[ht]
\centering
    \includegraphics{testbed/testbed1.pdf}
    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane. However, the fiber over a singular point of $B$ has an interesting structure. Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
    \label{fig:different_fibres}
\end{figure}
We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}

On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}. In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.

At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame. This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Corollary~\ref{cor:borel_reg_ODE}). As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$. Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations analytically in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).

@@

In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$. Generic directions correspond to $\theta\neq \arg (\alpha-\beta)$. } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$. Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha-\beta)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).

@@

When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The half-plane $z \in H_{\theta}$ in $T_b^*B^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T_b^*B$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
